Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-28 paper/motivation.tex
updating figures to match code more closely

We can now see how devising correct configurations for real, larger networks can be a nightmare. Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several geography-, neighbor- or prefix-based exceptions to the default behavior. Templates help by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually.
\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.

>>>>

We can now see how devising correct configurations for real, larger networks can quickly become a nightmare. Such networks have many neighbors across multiple commercial-relationship classes, differing numbers of links per neighbor, along with several geography-, neighbor- or prefix-based exceptions to the default behavior. For example, a large AS with many peers in different geographic locations, may be faced with complex challenges like keeping traffic within national boundaries.
Templates help to an extent by keeping preference and community values consistent across routers, but operators must still do much of the conceptually difficult work manually. 
%\sysname lets operators express such policies easily and intuitively. It then automatically generates per-device import and export filters, local preferences, MED attributes, and community tags to ensure that the policy is implemented correctly under all failure scenarios.
